---
title: "LABEX"
author: "Namratha"
date: "21 December 2017"
output: html_document
---

```{r}
stud<-read.csv("C:/Users/MURTHY/Downloads/Q2a.csv",header=T)
print(names(stud))
stud

```

Extract each dept students names separately
```{r}

aggregate(Names~Dept,stud,toString)

```


Extract students who have scored above 9 SGPA in each dept
```{r}
s1<-stud[stud$SGPA>=9,c("Names","Dept")]
aggregate(Names~Dept,s1,toString)
```

E. Store students marks numerically, transform into grades and store in new data frame

```{r}
calculateGrade<-function(mark)
{
  m<-c()
  for(x in mark)
  {
    if(x>=80 & x<90){
      res<-"A"
    }
    else if(x>=60 & x<80){
      res<-"B"
    }
    else if(x>=40 & x<60){
      res<-"C"
    }
    else if(x>=90){
      res<-"S"
    }
    else{
      res<-"D"
    }
    
    m<-c(m,res)
  }
  
  m
}

for(i in 1:nrow(stud))
{
  s1<-stud[,"Sub1"]
  s2<-stud[,"Sub2"]
  s3<-stud[,"Sub3"]
  s4<-stud[,"Sub4"]
  s5<-stud[,"Sub5"]
  g1=calculateGrade(s1)
  g2=calculateGrade(s2)
  g3=calculateGrade(s3)
  g4=calculateGrade(s4)
  g5=calculateGrade(s5)
}
ans<-data.frame(stud$Names,stud$USN,stud$Dept,g1,g2,g3,g4,g5,stud$SGPA)
ans

```

Extract S grade scores in all subjects in each dept separately.

```{r}
s<-ans[ans$g1=="S"|ans$g2=="S"|ans$g3=="S"|ans$g4=="S"|ans$g5=="S",c("stud.Names","stud.Dept")]
s
```

Extract students who have scored at least S grades in any 2 subjects
```{r}
ans[rowSums(ans=="S")>=1,c("stud.Names","stud.Dept")]

```
Check whether students grades are identical or not in each subject

```{r}

identical(student$Sub1,student$Sub2,student$Sub3,student$Sub4,student$Sub5)

```
























