---
title: "External 8"
author: "Namratha"
date: "21 December 2017"
output: html_document
---

Store all dept faculty names with designation, number of papers published, training programs attended and salary details.
```{r}

faculty<-read.csv("Q3a.csv",header=T)
names(faculty)
faculty

```

A. Plot, in each dept, how many faculty are earning more than 1 lakh.

```{r}

f<-faculty[faculty$Salary>100000, c("Name","Dept")]
plot(f$Dept)

```

B.Create subset of faculty, who have published more than 10 papers and their designation is Associate professor.

```{r}

sub<-subset(faculty,faculty$Papers.Published>5 & faculty$Designation=="Assosciate Professor")
sub

```

C.Find out average papers published by each dept, designation wise and Find out Average training programs attended by faculty each dept wise.

```{r}

aggregate(Papers.Published~Dept,faculty,mean)
aggregate(Training~Dept,faculty,mean)

```

D.Extract top 3 performers among faculty dept wise(who have more papers published and more training programmes attended)

```{r}

ff<-faculty[order(-faculty$Papers.Published-faculty$Training),]
ff

cs<-ff[ff$Dept=="CSE",]
csq<-data.frame(cs[1:3,c("Name","Dept","Training","Papers.Published")])
csq


```

E.Sort faculty details ,dept wise separately.

```{r}
faculty[order(faculty$Dept,faculty$Name),]

```

F.Search for faculty name in the data set and retrieve his/her details.

```{r}
subset(faculty,Name=="Mithra")
```
