---
title: "external 7"
author: "Namratha"
date: "21 December 2017"
output: html_document
---

Store all dept (9 depts) students names,USN,Dept names, 5 subject marks , grades and SGPA in csv file using ms excel. 
```{r}
stud<-read.csv("Q1a.csv",header=T)
names(stud)
stud
```


A.Plot , in each dept, how many students have scored above 9 SGPA
```{r}
s<-stud[stud$SGPA>=9,c("Names","Dept")]
s
plot(s$Dept)
```

B.Create subset of students , who have scored S grade in any subject and failed in any subject.
```{r}

sub<- subset(stud,rowSums(stud=="S")>=1 & rowSums(stud=="F")>=1)
sub

```

C.Find out average SGPA of each dept students and find out average score of each subject for each dept.

```{r}

aggregate(SGPA~Dept,stud,mean)
aggregate(as.numeric(Sub1)~Dept,stud,mean)

```

D.Extract 10 toppers of each dept.

```{r}

s<-stud[order(-stud$SGPA),]
 
b<-s[s$Dept=="BT",]
qb<-data.frame(b[1:3,c("Names","Dept","SGPA")])
qb


```

E.Sort students details of each dept separately.

```{r}

stud[order(stud$Dept),]

```


F.Search for a particular student name in the data set, and retrieve his/her details.

```{r}
subset(stud,Names=="Aravind")

```

















































































































