---
title: "External 9"
author: "Namratha"
date: "21 December 2017"
output: html_document
---

Store all dept faculty names with designation,  number of papers published, training programs attended and salary details.

```{r}

faculty<-read.csv("Llaabb-4.csv",header=T)
names(faculty)
faculty

```

A. Change the column names of faculty data set.

```{r}

colnames(faculty)<-c("Names","Desig","Sal","Dept","Trainings","Papers","Gender")
summary(faculty)

```

B. Use map values() , as.factor() and transform () to change the designation column to have numerical values. 1- Prof, 2-Asso.Prof, 3-Asst.Prof;to change gender column 1-Male, 2-Female

```{r}

library(plyr)
f<-transform(faculty,
             Desig=as.factor(mapvalues(Desig,c("Professor","Assosciate Professor","Assistant Professor"),c(1,2,3))),
             Gender=as.factor(mapvalues(Gender,c("M","F"),c(1,2))))
f

```

C.Using with() and tapply() , calculate the mean training programs attended and no. of papers published in each department. Format it for markdown.

```{r}

library(knitr)
library(rmarkdown)

kable(with(f , tapply(Trainings, INDEX=list(Dept,Papers), FUN =mean)), format="markdown")

kable(with(f , tapply(Trainings, INDEX=list(Dept,Gender), FUN=mean)) , format="markdown")

kable(with(f, tapply(Trainings, INDEX = list(Dept,Gender), FUN=sum)), format = "markdown")

```

D. Using with() and aggregate() , calculate the mean training programs attended and no. of papers published in each department. Format it for markdown.

```{r}

kable(with(f, aggregate(Trainings, by=list(Dept,Papers), FUN=mean)), format = "markdown")

kable(with(f, aggregate(Trainings, by=list(Dept,Gender), FUN=mean)), format = "markdown")

kable(with(f, aggregate(Trainings, by=list(Dept,Gender), FUN=mean)), format = "markdown")

```

E.Check whether the mean value of no. of papers published in depts. are influenced by training programs attended and designation. 

```{r}

aggregate(Papers~Trainings+Desig, FUN = mean, data=f)

```

F. Do regression analysis using aggregate() for faculty performance.

```{r}

aggregate(Trainings+Papers~Desig+Dept, data=faculty, FUN = toString)

```

























































































































