---
title: "External 2"
author: "Namratha"
date: "21 December 2017"
output: html_document
---

Store all dept faculty names with designation, number of papers published, training programs attended  and salary details.

```{r}
faculty<-read.csv("Q3a.csv",header=T)
names(faculty)
faculty
```

A. Extract each dept faculty details separately
```{r}
aggregate(Name~Dept,faculty,toString)

```

B.Extract Professors of each dept separately
```{r}

prof<-faculty[faculty$Designation=="Professor",c("Name","Dept","Salary")]
aggregate(Name~Dept,prof,toString)

```

C.Extract people who earn more than 1.5 lakh in each dept where their designation is prof, associate or assistant
```{r}

ppp<-faculty[faculty$Salary>="150000",c("Name","Dept")]
aggregate(Name~Dept,ppp,toString)

```

D. Find out the cost of professors in each dept .(sum up their salary to get cost of them)
```{r}

aggregate(Salary~Dept,prof,sum)

```

E.Find the individual cost of each dept faculty and average cost of faculty in dept
```{r}
SSal<-aggregate(Salary~Dept,faculty,sum)
MSal<-aggregate(Salary~Dept,faculty,mean)
SSal
MSal
```

F.Find out Which dept has highest average cost of faculty and which dept has lowest cost of faculty
```{r}

MSal[which.max(MSal$Salary),]
MSal[which.min(MSal$Salary),]


```



