---
title: "EXTERNAL 5"
author: "Namratha"
date: "21 December 2017"
output: html_document
---

Store all dept faculty names with designation, number of papers published, training programs attended and salary detail

```{r}
faculty<-read.csv("Q3a.csv",header=T)
faculty

```
A. Store faculty salary numerically, transform into factor.

```{r}

fac_cut<- cut(faculty$Salary, breaks = c(50000,75000,10000,Inf))
str(fac_cut)
```

B.Check whether faculty paper publication count and number of training program attended are same or not.
```{r}

identical(faculty$Papers.Published,faculty$Training)

```

C.Extract paper published count separately. If the count is greater than 15 map it as "Excellent", if it is (10-15 )map it as "good", if it is (5 to 10) map it as " moderate"), if it is (1-5) map it as "need to improve", else "poor, start your research".

```{r}
assignComment<-function(x)
{
  if(x>=15)
    res<-"Excellent"
  else if(x>=10)
    res<-Good
  else if(x>=5)
    res<-"Moderate"
  else if(x>=1)
    res<-"Need to improve"
  else
    res<-" Start research"
  
  res
}

for(i in 1:nrow(faculty))
{
  papers<-faculty[i,"Papers.Published"]
  ans<-assignComment(papers)
  faculty[i,"Comment"]<-ans
}

faculty

```

D. Consider the solution of (c ). Map "Excellent", "good" as " Good performers";Map " Moderate" and "need to improve" as " Ok, Keep it up". Else " map to " You may be fired!"

```{r}

assignImplication<-function(x)
{
 if(x =="Excellent"| x=="Good") 
    res <- "Good Perfformers"
 else if(x =="Moderate" | x=="Need to improve") 
    res <- "Ok,Keep it up"
 else
    res<-"You may be fired!"
  
  res
}
for(i in 1:nrow(faculty))
{
 comment<-faculty[i,"Comment"]
 ans<-assignImplication(comment)
 faculty[i,"Implication"]<-ans
 }
 
faculty

```

E. Transform designations to numerical data

```{r}

fac1<-transform(faculty, Designation=as.numeric(Designation))
fac1

```








































































































