Store all dept faculty names with designation,  number of papers published, training programs attended and salary details.

```{r}

faculty<-read.csv("Q3a.csv",header=T)
names(faculty)
colnames(faculty)<-c("Name", "Desig","Salary","Dept","Training", "Papers" )
faculty

```

A. Create the table output for designation and papers published. Use with() and table().
```{r}
ans<-with(faculty,table(Papers,Desig))
ans
```

B>Find the odds of lower no. of paper published with respect to designation and no.of training programs attended

```{r}

ans.or<-(ans[6,3]+ans[5,3]+ans[4,3]+ans[3,3]+ans[2,3]+ans[1,3])/(ans[6,2]+ans[5,2]+ans[4,2]+ans[3,2]+ans[2,2]+ans[1,2])/(ans[6,1]+ans[5,1]+ans[4,1]+ans[3,1]+ans[2,1]+ans[1,1])
ans.or

```

C. Is the designation affects the training programs attended? Check it with the data. Prove it.

```{r}
with(faculty, cor(as.numeric(Desig),Training))
```

D. Find the correlation of papers published and training programs attended using with(), cor().

```{r}
with(faculty,cor(Papers, Training))
```

E. Find the correlation of training programs attended and designation using with(), cor().
```{r}
with(faculty,cor(Training,as.numeric(Desig)))
```

F. Using by() combine the operations of above questions (d) and (e) using function. And do the correlation analysis using cor() with in the function.

```{r}

by(data=faculty[c("Papers","Training")] ,
   INDICES = faculty["Desig"] ,
   FUN = function(x){ cor(x[,1],x[,2]) } 
   )


```





























































































































































































