---
title: "external 4"
author: "Namratha"
date: "21 December 2017"
output: html_document
---

Store all dept (9 depts) students names,USN,Dept names, 5 subject marks , grades and SGPA in csv file using ms excel. 
```{r}
stud<-read.csv("Q2a.csv",header=T)
names(stud)
stud
```

A. Create table from student data with USN and names only.
```{r}
stud[c("Names","USN")]
#table(stud$Names,stud$USN)
```

B.Display the typeof each column.
```{r}
sapply(student,typeof)
```

C. Write a function to provide recommendations of students about their performance in the exams  like "Good", "Moderate", "Need improvement" ,etc., 
```{r}
assignComment<-function(mark)
{
  x<-sum(mark)/5
  
  if(x>=80)
    res<-"Good"
  else if(x>=60 & x<80)
    res<-"Moderate"
  else if (x>=40)
    res<-"Need improvement"
  else
    res<-"Poor"
  
  res
 }


for (i in 1:nrow(stud)) 
{
  s1<-stud[i,"Sub1"]
  s2<-stud[i,"Sub2"]
  s3<-stud[i,"Sub3"]
  s4<-stud[i,"Sub4"]
  s5<-stud[i,"Sub5"]
  
  mark<-c(s1,s2,s3,s4,s5)
  ans<-assignComment(mark)
  
  stud[i,"Comment"]<-ans
}

stud
```
D. Write a function to perform statistical analysis of students data.

```{r}

Summary_sub<-function(x)
{
  res<-c(mean=mean(x),median=median(x),sd=sd(x))
  res
}

sub2<-stud$Sub2
ans<-Summary_sub(sub2)
ans

```

E. Use sapply to perform ( c ) and  ( d )

```{r}

assignResult<-function(x)
{
  
  if(x>=80)
    res<-"Good"
  else if(x>=60 & x<80)
    res<-"Moderate"
  else if (x>=40)
    res<-"Need improvement"
  else
    res<-"Poor"
  
  res
}

sub1<-stud$Sub1
ans<-sapply(sub1,FUN = assignResult)
ans
ans2<-sapply(sub2,FUN = Summary_sub)
ans2

```























