
Store all dept faculty names with designation, number of papers published, training programs attended and salary detail

```{r}
faculty<-read.csv("Q3a.csv",header=T)
faculty

```

A. Using factor() and mapvalues() convert designations to numerical data.

```{r}

fac2<-transform(faculty,
                Designation=as.factor(
                  mapvalues(Designation,
                            c("Professor","Assistant Professor","Assosciate Professor"),
                            c(1,2,3))))
fac2

```

B.Create table for faculty names and designations.

```{r}
table(faculty$Name,faculty$Designation)
```

C.Write a function to provide recommendation about faculty performance based on the number of papers published and number of training programs attended. Like Good, Moderate, Need improvement .

```{r}

assignComment <- function(x) 
{
 if(x >= 15) {
    res <- "Excellent"
  } else if(x >= 10 & x<15) {
    res <- "Good"
  } else if(x >= 5 & x<10) {
    res <- "Moderate"
  } else if(x>=1 & x<5){
    res <- "Need to improve"
  }
  else{
    res<-"Poor,start your research"
  }
  res
}
for(i in 1:nrow(faculty))
{
 papers<-faculty[i,"Papers.Published"]
 ans<-assignComment(papers)
 faculty[i,"Comment"]<-ans
 }
 
faculty

```

D.Write a function to perform statistical analysis of faculty data to identify faculty performance of depts.

```{r}

Summary_fac<-function(x)
{
  ans<-c(mean=mean(x), median=median(x), sd=sd(x))
  ans

}

Summary_fac(faculty$Training)

```

E.Use sapply to perform all the above functions.

```{r}

assignComment<-function(x)
{
  if(x>=15)
    res<-"Excellent"
  else if(x>=10)
    res<-Good
  else if(x>=5)
    res<-"Moderate"
  else if(x>=1)
    res<-"Need to improve"
  else
    res<-" Start research"
  
  res
}

papers<-faculty[,"Papers.Published"]
ans<-sapply(papers,FUN=assignComment)
f<-data.frame(faculty$Name,ans)
f


assignImplication<-function(x)
{
 if(x =="Excellent"| x=="Good") 
    res <- "Good Perfformers"
 else if(x =="Moderate" | x=="Need to improve") 
    res <- "Ok,Keep it up"
 else
    res<-"You may be fired!"
  
  res
}

comment<-f[,"ans"]
ans<-sapply(comment, FUN=assignImplication)
f2<-data.frame(faculty$Name, ans)
f2

```



























































