Store all dept (9 depts) students names,USN,Dept names, 5 subject marks , grades and SGPA in csv file using ms excel. 

```{r}

stud<-read.csv("Tut-3.csv",header=T)
stud

```



A. Make some string entries in student marks. Make some numerical entries in names.
```{r}
x <- data.frame("SN" = 1:2, "Age" = c(21,15), "Name" = c("John","Dora"))
	
str(x) 
	
```

B.Using gsub remove character data in marks column. Using gsub remove numerical data in name column

```{r}

sub2=stud$Sub2
sub2
gsub("[^0-9]","",sub2)

name<-stud$ï..Names
gsub("[^a-zA-Z]","",name)


```

C.Clean the name and marks column and put it in a new student data set variable using transform function

```{r}

sub2.clean<-gsub("[^0-9]","",sub2)
newstud<-transform(stud,Sub2= sub2.clean)
newstud

```

D. Use table to get summary of student data
```{r}

table(student["Sub1"])
table(student["Dept"])

```


E.Use sapply to perform the cleaning of data mentioned above

```{r}
clean<-function(student)
{
  sub2.clean <- as.numeric(gsub("[^0-9.]", "", sub2))
  sub2.clean
  new_stud<-transform(student, Sub2 = sub2.clean)
  new_stud
}

sapply(student,FUN=clean)

```



Use lapply to perform the cleaning of data mentioned above.

```{r}
lapply(stud,FUN=clean)


```




































































































