Store all dept faculty names with designation,  number of papers published, training programs attended and salary details.

```{r}

faculty<-read.csv("Q3a.csv",header=T)
names(faculty)
#faculty

```

A. Plot average training programs attended against designations(only 3 designations)  of the institution using plot()

```{r}

f1<-aggregate(Training~Designation,faculty,mean)
plot(f1$Designation, f1$Training)

```

B. Plot average papers published against designations of  the institution using plot().

```{r}

f2<-aggregate(Papers.Published~Designation,faculty,mean)
f2
plot(f2$Designation, f2$Papers.Published)

```

C. Plot the graphs of (a) and (b) using with() and plot().

```{r}

#par(mfrow=c(1,2))

with(faculty, plot(Designation, Training , main = "Designation vs Trainings", xlab = "Designation",  ylab = "Tranings",col=7))

with(faculty, plot(Designation, Papers.Published, 
                   main = "Designation vs Papers Published", 
                   xlab = "Designation", 
                    ylab = "Papers Published ",col=8))


```

D. Change the x axis , color and y-axis labels respectively.  Add legends. 
```{r}

plot(f2$Desig, f2$Papers,xlab="Designation",ylab="Papers Published",main="Designation vs Papers Published",col=5)

```

E.Draw scatter plot for above questions. Draw box plot for above question.  Draw bar plots for above questions. Draw single variable plots for above questions.

```{r}

with(faculty, boxplot(as.numeric(Designation), Training , 
                      main=" Designation vs Training" ,
                      xlab="Designation",
                      ylab="Training", col=1))

with(f, boxplot(as.numeric(Desig), Papers,
              main = "Designation vs Papers Published",
              xlab = "Designation",
              ylab = "Papers Published ",col=2))


with(f, barplot(as.numeric(Desig), Trainings,
              main = "Designation vs Trainings",
              xlab = "Designation",
              ylab = "Tranings",col=3))
with(f, barplot(as.numeric(Desig), Papers,
              main = "Designation vs Papers Published",
              xlab = "Designation",
              ylab = "Papers Published ",col=4))

```

F. Plot the prof, asst.prof and asso.prof average performance in different colors using rep(), colorpalatte() functions. Represent each designation average performance by different symbols.

```{r}

c1<-subset(faculty,Designation=="Assosciate Professor", c("Papers.Published","Training"))
y1<-mean(c1$Papers.Published+ c1$Training)

c2<-subset(faculty,Designation=="Assistant Professor",    c("Papers.Published","Training"))
y2<-mean(c2$Papers.Published+c2$Training)

c3<-subset(faculty,Designation=="Professor",
           c("Papers.Published","Training"))
y3<-mean(c3$Papers.Published+c3$Training)

x<-c(1,2,3)
y<-c(y1,y2,y3)

p<-c(19,23,15)
 plot(x, y, main = "avg performance", 
                   xlab = "assoc prof", 
                   ylab = "Tranings",col=palette(),pch=p)
 
 with(f,text( x =1 ,y=y1, labels ="assoc prof",
                pos = rep(c(1, 3, 1), c(5, 1, 2)))) 


  with(f,text(x =2,y=y2, labels ="assis prof",
                pos = rep(c(1, 3, 1), c(5, 1, 2)))) 
  with(f,text(x =3,y=y3, labels ="prof",
                pos = rep(c(1, 3, 1), c(5, 1, 2)))) 

```








































































































































































































